Mirror, mirror on the wall. Which's the best match of them all?

### 2024-01-19 PNAS/index.Rnw
line 102

In order to calculate the number of possible comparisons to be carried out in the course of the examination, we define $\ell$ to be the length of the blade cut, and $d$ to be the diameter of the wire. Without loss of generality, we assume that the wire is fully covered with striations suitable for comparison; if this is not the case, we adjust the value of $d$.
An illustration of the sliding comparison process is shown in \Cref{fig:wire-blade}. Imagine that you start from the left end of the blade and move the wire surface $d$ units at a time along the blade.
At minimum, there must be $\ell/d$ comparisons in order to assess whether one side of the blade cut matches one side of the wire; in this case, the comparisons are physically separate and thus expected to be statistically independent, though empirically there will be nonzero correlations due to the physical similarities between striations.
%no overlapping data is used.
This method of counting the number of comparisons assumes
perfect alignment between the diameter of the wire and the portion of the blade used to cut the wire, which is unrealistic but provides us with a lower bound.

>>>>

In order to calculate the number of comparisons carried out in the course of one examination, we define $\ell$ to be the length of the blade cut, and $d$ to be the diameter of the wire. We assume that the wire is covered with striations suitable for comparison across its full diameter $d$. If this is not the case, we reduce the value $d$ correspondingly.
An illustration of the sliding comparison process is shown in \Cref{fig:wire-blade}. Imagine that you start from the left end of the blade and move the wire surface $d$ units at a time along the blade.

At minimum, there must be $\ell/d$ comparisons in order to assess whether one side of the blade cut matches one side of the wire; in this case, the comparisons are physically separate and thus expected to be statistically independent, though empirically there will be nonzero correlations due to the physical similarities between striations.
%no overlapping data is used.
This method of counting the number of comparisons assumes
perfect alignment between the diameter of the wire and the portion of the blade used to cut the wire, which is unrealistic but provides us with a lower bound.
